Fully Automatic Loop-free Program Synthesis by Bounded Model Checking

### 2013-10-11 paper/paper.tex
Changed results table to be included

\begin{figure}
\begin{center}

\begin{tabular}{l|r|r|r|r}
Problem & {\sc Brahma} & {\sc Kalashnikov} & {\sc Kalashnikov} & {\sc Kalashnikov} \\
        &               &                    & (no width)         & (CBMC only) \\
\hline
p1 & 3.20s &{\bf 1.83s} &23.54s &8.07s \\
p2 & 3.60s &{\bf 1.49s} &1271.12s &8.19s \\
p3 & {\bf 1.40s} &1.60s &4.09s &5.90s \\
p4 & 3.30s &{\bf 1.86s} &79.72s &8.15s \\
p5 & 2.20s &{\bf 1.98s} &12.16s &8.10s \\
p6 & 2.40s &{\bf 1.51s} &104.19s &8.17s \\
p7 & {\bf 1.00s} &4.04s &-- &14.49s \\
p8 & {\bf 1.40s} &4.31s &-- &14.20s \\
p9 & {\bf 5.80s} &13.64s &505.10s &13.45s \\
p10 & 76.10s &{\bf 9.80s} &-- &19.14s \\
p11 & 57.10s &{\bf 9.40s} &{\bf 9.40s} &32.98s \\
p12 & 67.80s &{\bf 21.43s} &{\bf 21.43s} &38.23s \\
p13 & {\bf 6.20s} &8.90s &27.74s &13.16s \\
p14 & 59.60s &54.71s &54.71s &{\bf 52.69s} \\
p15 & 118.90s &{\bf 43.49s} &{\bf 43.49s} &44.31s \\
p16 & 62.30s &{\bf 27.41s} &{\bf 27.41s} &45.84s \\
p17 & 78.10s &{\bf 27.73s} &{\bf 27.73s} &46.63s \\
p18 & 45.90s &{\bf 5.55s} &{\bf 5.55s} &15.63s \\
p19 & {\bf 34.70s} &-- &-- &-- \\
p20 & {\bf 108.40s} &-- &-- &-- \\
p21 & {\bf 28.30s} &-- &-- &-- \\
p22 & {\bf 279.00s} &-- &-- &-- \\
p23 & {\bf 1668.00s} &-- &-- &-- \\
p24 & {\bf 224.90s} &-- &-- &-- \\
p25 & {\bf 2778.70s} &-- &-- &-- \\
\end{tabular}

\end{center}

\caption{Times for synthesis of machine integer benchmarks from {\sc brahma} paper}
\label{fig:results-table}

>>>>

\begin{figure}
\begin{center}
\include{figures/results_table}
\end{center}

\caption{Times for synthesis of machine integer benchmarks from {\sc brahma} PLDI paper}
\label{fig:results-table}
\end{figure}

\begin{figure}
\begin{center}
\include{figures/icse_results_table}
\end{center}

\caption{Times for synthesis of machine integer benchmarks from {\sc brahma} ICSE paper}
\label{fig:icse-results-table}
\end{figure}
